Figures for Paper

### 2021-02-24 paper_figures.Rmd
Add code for generating side by side stmn2 unc13a graph

```{r}
clean_data_table = fread(file.path(here::here(),"data","nygc_junction_information.csv"))
clean_data_table = clean_data_table %>%     
    mutate(call = fct_relevel(call,
                              "C/C", "C/G", "G/G")) %>% 
    mutate(number_g_alleles = as.numeric(call) - 1) %>% 
    mutate(unc13a_cryptic_leaf_psi = ifelse(is.na(unc13a_cryptic_leaf_psi),0,unc13a_cryptic_leaf_psi))

print(glue::glue("Number of unique patients: {clean_data_table[,length(unique(participant_id))]}"))
print(glue::glue("Number of unique tissue samples: {clean_data_table[,length(unique(sample))]}"))
print("Patients Per Disease Category")
clean_data_table[,length(unique(participant_id)),by = disease]
print("Tissues Per Disease Category")
clean_data_table[,length(unique(sample)),by = disease]
print("Number of patients per rs12973192 genotype")
clean_data_table[,length(unique(participant_id)),by = call]
print("Number of tissues per disease")
clean_data_table[,.N,by = c("disease","tissue_clean")]
print("Number of partcipants by mutation and  disease")
clean_data_table[,length(unique(participant_id)),by = c("mutations","disease")]

@@

boxplot_table %>% 
  left_join(clean_data_table %>% dplyr::select(sample, call)) %>% 
  unique() %>% 
  filter(!(tissue_clean %in% c("Cerebellum","Hippocampus","Occipital Cortex"))) %>% 
  mutate(detected = inclusion_reads > 0) %>% 
  dplyr::select(sample,disease_group2,detected,tissue_clean,call) %>% 
  unique() %>% 
  group_by(disease_group2,tissue_clean,call) %>% 
  mutate(n_sample = n_distinct(sample)) %>% 
  mutate(n_sample_detected = sum(detected)) %>% 
  dplyr::select(tissue_clean,disease_group2,n_sample,n_sample_detected) %>% 
  unique() %>% 
  mutate(detection_rate = n_sample_detected / n_sample) %>% 
  mutate(disease_group2 = gsub("Control"," Control",disease_group2)) %>% 
  ungroup() %>% 
  filter(grepl("ALS-TDP|FTLD-T",disease_group2)) %>% 
  mutate(tissue_clean = fct_relevel(tissue_clean, "Cervical Spinal Cord",
                                    "Frontal Cortex",
                                    "Lumbar Spinal Cord",
                                    "Motor Cortex",
                                    "Thoracic Spinal Cord")) %>% 
    mutate(detection_name = glue::glue("{disease_group2} \n ( {n_sample} )")) %>% 
  mutate(cortex = ifelse(grepl(" Cord",tissue_clean),"cot","cor")) %>% 
  ggplot() +
  geom_col(aes(x = detection_name, y = detection_rate,fill = call),position = position_dodge2(width = 0.8, preserve = "single")) + 
  ggpubr::theme_pubr() + 
  ylab("Percent of Tissues \n UNC13A Cryptic Detected") + 
  theme(text = element_text(size = 18)) + 
  xlab("N tissues") + 
  facet_wrap(~tissue_clean,scales = 'free_x',nrow = 3) +
    scale_y_continuous(lim = c(0,1),labels = scales::percent,expand = c(0,0) ) + 
  theme(axis.text.x =  element_text(size = 14)) + 
      theme_bw() + 
    theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank()) + 
  theme(text = element_text(size = 18))  +
  theme(legend.position = "bottom") 
```

@@

# Relationship between STMN2 and UNC13A CE PSI in patients
```{r}
####scatter plot showing the correlation in non-log space in STMN2 and cryptic PSI####
clean_data_table %>% 
  filter(disease_tissue == T) %>% 
  filter(disease_group2 %in% c("FTLD-TDP","ALS-TDP")) %>% 
  filter(grepl("Cortex",tissue_clean)) %>% 
  filter(stmn_2_cryptic_psi_leaf > 0 ) %>% 
  filter(unc13a_cryptic_leaf_psi > 0) %>% 
  ggplot(aes(x = stmn_2_cryptic_psi_leaf, y = unc13a_cryptic_leaf_psi)) + 
  geom_point() + 
  stat_cor(size = 8,method = "spearman",cor.coef.name = "rho") + 
  geom_smooth(method = lm, se = FALSE,color = "black") +
  xlab("STMN2 Cryptic PSI") +
  ylab("UNC13A CE PSI") + 
  ggpubr::theme_pubr() + 
  theme(text = element_text(size = 18)) +
  scale_y_continuous(labels = scales::percent)  +
  scale_x_continuous(labels = scales::percent) 
```

@@

clean_data_table %>% 
  filter(disease_tissue == T) %>% 
  filter(disease_group2 %in% c("FTLD-TDP","ALS-TDP")) %>% 
  dplyr::select(sample,tissue_clean,disease_group2,call,stmn_2_cryptic_psi_leaf,unc13a_cryptic_leaf_psi) %>% 
  mutate(tissue_clean = gsub("_"," ",tissue_clean)) %>% 
  group_by(call) %>% 
  mutate(n_sample = length(unique(sample))) %>% 
  ungroup() %>% 
  mutate(detection_name = glue::glue("{call} \n ( {n_sample} )")) %>% 
  ggplot(aes(y = unc13a_cryptic_leaf_psi, x = call, fill = call)) + 
  geom_boxplot() + 
  geom_jitter( height = 0) + 
  facet_wrap(~disease_group2,scales = 'free') +
  ylab("UNC13A PSI") +
  xlab("UNC13A rs12973192 Genotype") +
  scale_fill_manual(values = c("#88CCEE","#44AA99","#1B7739")) +
  ggpubr::theme_pubr() +
  theme(text = element_text(size = 24)) +
  stat_compare_means(comparisons = genotype_comparisons,label = "p.signif")

@@

clean_data_table %>% 
  filter(disease_tissue == T) %>% 
  filter(disease_group2 %in% c("FTLD-TDP","ALS-TDP")) %>% 
  dplyr::select(sample,tissue_clean,disease_group2,call,stmn_2_cryptic_psi_leaf,unc13a_cryptic_leaf_psi) %>% 
  mutate(tissue_clean = gsub("_"," ",tissue_clean)) %>% 
  group_by(call) %>% 
  mutate(n_sample = length(unique(sample))) %>% 
  ungroup() %>% 
  mutate(detection_name = glue::glue("{call} \n ( {n_sample} )")) %>% 
  ggplot(aes(y = unc13a_cryptic_leaf_psi, x = call, fill = call)) + 
  geom_boxplot() + 
  geom_jitter( height = 0) + 
  facet_wrap(~disease_group2 + tissue_clean,scales = 'free') +
  ylab("UNC13A PSI") +
  xlab("UNC13A rs12973192 Genotype") +
  scale_fill_manual(values = c("#88CCEE","#44AA99","#1B7739")) +
  ggpubr::theme_pubr() +
  theme(text = element_text(size = 24)) +
  stat_compare_means(comparisons = genotype_comparisons,label = "p.signif")

@@

clean_data_table %>% 
  filter(unc13a_cryptic_leaf_psi > 0 ) %>% 
  filter(disease_tissue == T) %>% 
  filter(disease_group2 %in% c("FTLD-TDP","ALS-TDP")) %>% 
  dplyr::select(sample,tissue_clean,disease_group2,call,stmn_2_cryptic_psi_leaf,unc13a_cryptic_leaf_psi) %>% 
  mutate(tissue_clean = gsub("_"," ",tissue_clean)) %>% 
  group_by(call) %>% 
  mutate(n_sample = length(unique(sample))) %>% 
  ungroup() %>% 
  mutate(detection_name = glue::glue("{call} \n ( {n_sample} )")) %>% 
  ggplot(aes(y = unc13a_cryptic_leaf_psi, x = call, fill = call)) + 
  geom_boxplot() + 
  geom_jitter( height = 0) + 
  facet_wrap(~disease_group2 + tissue_clean,scales = 'free') +
  ylab("UNC13A PSI") +
  xlab("UNC13A rs12973192 Genotype") +
  scale_fill_manual(values = c("#88CCEE","#44AA99","#1B7739")) +
  ggpubr::theme_pubr() +
  theme(text = element_text(size = 24)) +
  stat_compare_means(comparisons = genotype_comparisons,label = "p.signif")

@@

clean_data_table %>% 
  filter(disease_tissue == T) %>% 
  filter(disease_group2 %in% c("FTLD-TDP","ALS-TDP")) %>% 
  dplyr::select(sample,tissue_clean,disease_group2,call,stmn_2_cryptic_psi_leaf,unc13a_cryptic_leaf_psi) %>% 
  mutate(tissue_clean = gsub("_"," ",tissue_clean)) %>% 
  ggplot(aes(y = stmn_2_cryptic_psi_leaf, x = call, fill = call)) + 
  geom_boxplot() + 
  geom_jitter( height = 0) + 
  facet_wrap(~disease_group2,scales = 'free') +
  ylab("STMN2 PSI") +
  xlab("UNC13A rs12973192 Genotype") +
  scale_fill_manual(values = c("#88CCEE","#44AA99","#1B7739")) +
  ggpubr::theme_pubr() +
  theme(text = element_text(size = 24)) +
  stat_compare_means(comparisons = genotype_comparisons,label = "p.signif")

@@

clean_data_table %>% 
  filter(disease_tissue == T) %>% 
  filter(disease_group2 %in% c("FTLD-TDP","ALS-TDP")) %>% 
  dplyr::select(sample,tissue_clean,disease_group2,call,stmn_2_cryptic_psi_leaf,unc13a_cryptic_leaf_psi) %>% 
  mutate(tissue_clean = gsub("_"," ",tissue_clean)) %>% 
  ggplot(aes(y = stmn_2_cryptic_psi_leaf, x = call, fill = call)) + 
  geom_boxplot() + 
  geom_jitter( height = 0) + 
  facet_wrap(~disease_group2 + tissue_clean,scales = 'free') +
  ylab("STMN2 PSI") +
  xlab("UNC13A rs12973192 Genotype") +
  scale_fill_manual(values = c("#88CCEE","#44AA99","#1B7739")) +
  ggpubr::theme_pubr() +
  theme(text = element_text(size = 24)) +
  stat_compare_means(comparisons = genotype_comparisons,label = "p.signif")

@@

clean_data_table %>% 
  filter(stmn_2_cryptic_psi_leaf > 0 ) %>% 
  filter(disease_tissue == T) %>% 
  filter(disease_group2 %in% c("FTLD-TDP","ALS-TDP")) %>% 
  dplyr::select(sample,tissue_clean,disease_group2,call,stmn_2_cryptic_psi_leaf,unc13a_cryptic_leaf_psi) %>% 
  mutate(tissue_clean = gsub("_"," ",tissue_clean)) %>% 
  ggplot(aes(y = stmn_2_cryptic_psi_leaf, x = call, fill = call)) + 
  geom_boxplot() + 
  geom_jitter( height = 0) + 
  facet_wrap(~disease_group2 + tissue_clean,scales = 'free') +
  ylab("STMN2 PSI") +
  xlab("UNC13A rs12973192 Genotype") +
  scale_fill_manual(values = c("#88CCEE","#44AA99","#1B7739")) +
  ggpubr::theme_pubr() +
  theme(text = element_text(size = 24)) +
  stat_compare_means(comparisons = genotype_comparisons,label = "p.signif")

@@

clean_data_table %>% 
  filter(disease_tissue == T) %>% 
  filter(grepl("Cortex",tissue_clean)) %>% 
  filter(disease_group2 %in% c("FTLD-TDP","ALS-TDP")) %>% 
    mutate(call = fct_relevel(call,
                              "C/C", "C/G", "G/G")) %>%
  filter(!grepl("Cord",tissue_clean)) %>% 
  mutate(log10_stmn2 = log10(stmn_2_cryptic_psi_leaf)) %>% 
    mutate(log10_unc13a = log10(unc13a_cryptic_leaf_psi)) %>% 
    ggpubr::ggscatter(., 
                      x = "log10_stmn2",
                      y = "log10_unc13a",
                      color = 'call',                      
                      add = "reg.line", size = 3
                      ) +
    ylab("UNC13A CE PSI ") + 
    xlab("STMN2 Cryptic PSI ") +
  stat_cor(aes( x = stmn_2_cryptic_psi_leaf,
                      y = unc13a_cryptic_leaf_psi,
                      color = call),
           method = 'spearman',
           cor.coef.name = 'rho',
           show.legend = FALSE,
           size = 14) + 
    scale_color_manual(values = c("#88CCEE","#44AA99","#1B7739")) +
  theme(legend.title = element_blank()) +
  theme(text = element_text(size = 24),legend.text = element_text(size = 32))

@@

## Log2 Fold UNC / STMN2 CE in TDP-path with both detected

>>>>

```{r}
clean_data_table = fread(file.path(here::here(),"data","nygc_junction_information.csv"))
clean_data_table = clean_data_table %>%     
    mutate(rs12973192 = fct_relevel(rs12973192,
                              "C/C", "C/G", "G/G")) %>% 
    mutate(number_g_alleles = as.numeric(rs12973192) - 1) %>% 
    mutate(unc13a_cryptic_leaf_psi = ifelse(is.na(unc13a_cryptic_leaf_psi),0,unc13a_cryptic_leaf_psi))

print(glue::glue("Number of unique patients: {clean_data_table[,length(unique(participant_id))]}"))
print(glue::glue("Number of unique tissue samples: {clean_data_table[,length(unique(sample))]}"))
print("Patients Per Disease Category")
clean_data_table[,length(unique(participant_id)),by = disease]
print("Tissues Per Disease Category")
clean_data_table[,length(unique(sample)),by = disease]
print("Number of patients per UNC13A SNP genotype")
unique(clean_data_table[,.(participant_id,rs12608932,rs12973192)]) %>% select(-participant_id) %>% table()
print("Number of tissues per disease")
clean_data_table[,.N,by = c("disease","tissue_clean")]
print("Number of partcipants by mutation and  disease")
clean_data_table[,length(unique(participant_id)),by = c("mutations","disease")]

@@

boxplot_table %>% 
  left_join(clean_data_table %>% dplyr::select(sample, rs12973192)) %>% 
  unique() %>% 
  filter(!(tissue_clean %in% c("Cerebellum","Hippocampus","Occipital Cortex"))) %>% 
  mutate(detected = inclusion_reads > 0) %>% 
  dplyr::select(sample,disease_group2,detected,tissue_clean,rs12973192) %>% 
  unique() %>% 
  group_by(disease_group2,tissue_clean,rs12973192) %>% 
  mutate(n_sample = n_distinct(sample)) %>% 
  mutate(n_sample_detected = sum(detected)) %>% 
  dplyr::select(tissue_clean,disease_group2,n_sample,n_sample_detected) %>% 
  unique() %>% 
  mutate(detection_rate = n_sample_detected / n_sample) %>% 
  mutate(disease_group2 = gsub("Control"," Control",disease_group2)) %>% 
  ungroup() %>% 
  filter(grepl("ALS-TDP|FTLD-T",disease_group2)) %>% 
  mutate(tissue_clean = fct_relevel(tissue_clean, "Cervical Spinal Cord",
                                    "Frontal Cortex",
                                    "Lumbar Spinal Cord",
                                    "Motor Cortex",
                                    "Thoracic Spinal Cord")) %>% 
    mutate(detection_name = glue::glue("{disease_group2} \n ( {n_sample} )")) %>% 
  mutate(cortex = ifelse(grepl(" Cord",tissue_clean),"cot","cor")) %>% 
  ggplot() +
  geom_col(aes(x = detection_name, y = detection_rate,fill = rs12973192),position = position_dodge2(width = 0.8, preserve = "single")) + 
  ggpubr::theme_pubr() + 
  ylab("Percent of Tissues \n UNC13A Cryptic Detected") + 
  theme(text = element_text(size = 18)) + 
  xlab("N tissues") + 
  facet_wrap(~tissue_clean,scales = 'free_x',nrow = 3) +
    scale_y_continuous(lim = c(0,1),labels = scales::percent,expand = c(0,0) ) + 
  theme(axis.text.x =  element_text(size = 14)) + 
      theme_bw() + 
    theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank()) + 
  theme(text = element_text(size = 18))  +
  theme(legend.position = "bottom") 
```

@@

# Relationship between STMN2 and UNC13A CE PSI 
## Scatter plot showing the correlation in non-log space in cortex UNC13A & STMN2 CE

```{r}
clean_data_table %>% 
  filter(disease_tissue == T) %>% 
  filter(disease_group2 %in% c("FTLD-TDP","ALS-TDP")) %>% 
  filter(grepl("Cortex",tissue_clean)) %>% 
  filter(stmn_2_cryptic_psi_leaf > 0 ) %>% 
  filter(unc13a_cryptic_leaf_psi > 0) %>% 
  ggplot(aes(x = stmn_2_cryptic_psi_leaf, y = unc13a_cryptic_leaf_psi)) + 
  geom_point() + 
  stat_cor(size = 8,method = "spearman",cor.coef.name = "rho") + 
  geom_smooth(method = lm, se = FALSE,color = "black") +
  xlab("STMN2 Cryptic PSI") +
  ylab("UNC13A CE PSI") + 
  ggpubr::theme_pubr() + 
  theme(text = element_text(size = 18)) +
  scale_y_continuous(labels = scales::percent)  +
  scale_x_continuous(labels = scales::percent) 
```

## Side by side comparison UNC13A & STMN2 CE PSI
```{r}
clean_data_table %>% 
  # filter(stmn_2_cryptic_psi_leaf > 0 ) %>% 
  # filter(unc13a_cryptic_leaf_psi > 0) %>% 
  filter(disease_tissue == T) %>% 
  filter(disease_group2 %in% c("FTLD-TDP","ALS-TDP")) %>% 
  dplyr::select(sample,disease_group2,tissue_clean,stmn_2_cryptic_psi_leaf,unc13a_cryptic_leaf_psi) %>% 
  melt() %>% 
  mutate(tissue_clean = gsub("_"," ",tissue_clean)) %>%
    mutate(tissue_clean = fct_relevel(tissue_clean,"Motor Cortex", "Cervical Spinal Cord",
                                    "Frontal Cortex",
                                    "Lumbar Spinal Cord",
                                    "Temporal Cortex")) %>% 
  mutate(variable = ifelse(grepl("stmn_2",variable), "STMN2", "UNC13A")) %>%
  ggplot(aes(x = variable, y = value)) +
  geom_boxplot(aes(color = variable)) +
  geom_jitter(aes(fill = variable),pch = 21,height = 0,width = 0.2,size = 3) +
  scale_fill_manual(values = c("#004D40","#882255")) +
  scale_color_manual(values = c("#004D40","#882255")) +
  facet_wrap(~tissue_clean,nrow = 3,scales = 'free') +
    scale_y_continuous(labels = scales::percent)  +
  ggpubr::theme_pubr() +
  theme(text = element_text(size = 24))  +
  xlab("") +
  ylab("PSI")  +
  theme(legend.position = 'none')

## Side by side comparison UNC13A & STMN2 CE PSI v2 
```{r}
clean_data_table %>% 
  filter(UNC13A_annotated_leaf > 10) %>% 
  filter(STMN2_annotated_leaf > 10) %>% 
  # filter(stmn_2_cryptic_psi_leaf > 0 ) %>%
  # filter(unc13a_cryptic_leaf_psi > 0) %>%
  # filter(disease_tissue == T) %>% 
    mutate(tissue_clean = gsub("_"," ",tissue_clean)) %>%
  filter(tissue_clean %in% c("Motor Cortex", "Cervical Spinal Cord", "Frontal Cortex", "Lumbar Spinal Cord", "Temporal Cortex")) %>% 
  filter(disease_group2 %in% c("FTLD-TDP","ALS-TDP")) %>% 
  dplyr::select(sample,disease_group2,tissue_clean,stmn_2_cryptic_psi_leaf,unc13a_cryptic_leaf_psi) %>% 
  mutate(log2_rat = log2((unc13a_cryptic_leaf_psi + 0.1) / (stmn_2_cryptic_psi_leaf + 0.1))) %>% 
  group_by(tissue_clean, disease_group2) %>% 
  mutate(average_log2Fold = mean(log2_rat)) %>% 
  ungroup() %>% 
  dplyr::select(-log2_rat) %>% 
  pivot_longer(cols = c("stmn_2_cryptic_psi_leaf","unc13a_cryptic_leaf_psi")) %>% 
  mutate(tissue_clean = fct_reorder(tissue_clean,average_log2Fold)) %>% 
  mutate(variable = ifelse(grepl("stmn_2",name), "STMN2", "UNC13A")) %>%
  ggplot(aes(x = tissue_clean, y = value,fill = name)) +
  geom_boxplot() +
  geom_point(pch = 21,height = 0,width = 0.2,position = position_jitterdodge()) +
  scale_fill_manual(values = c("#004D40","#882255")) +
  facet_wrap(~tissue_clean+disease_group2,nrow = 1,scales = 'free')  +
  theme(text = element_text(size = 24))  +
  xlab("") +
  ylab("PSI")  +
  theme(legend.position = 'none')
```

## Side by side comparison UNC13A & STMN2 CE PSI - v3
```{r}
clean_data_table %>% 
  # filter(stmn_2_cryptic_psi_leaf > 0 ) %>% 
  # filter(unc13a_cryptic_leaf_psi > 0) %>% 
  filter(disease_group2 %in% c("FTLD-TDP","ALS-TDP")) %>% 
  dplyr::select(sample,disease_group2,tissue_clean,stmn_2_cryptic_psi_leaf,unc13a_cryptic_leaf_psi) %>% 
  melt() %>% 
  mutate(tissue_clean = gsub("_"," ",tissue_clean)) %>%
    mutate(tissue_clean = fct_relevel(tissue_clean,"Motor Cortex", "Cervical Spinal Cord",
                                    "Frontal Cortex",
                                    "Lumbar Spinal Cord",
                                    "Temporal Cortex")) %>% 
  mutate(variable = ifelse(grepl("stmn_2",variable), "STMN2", "UNC13A")) %>%
  ggplot(aes(x = variable, y = value)) +
  geom_boxplot(aes(color = variable)) +
  geom_jitter(aes(fill = variable),pch = 21,height = 0,width = 0.2,size = 3) +
  scale_fill_manual(values = c("#004D40","#882255")) +
  scale_color_manual(values = c("#004D40","#882255")) +
  facet_wrap(~tissue_clean+disease_group2,nrow = 3,scales = 'free') +
    scale_y_continuous(labels = scales::percent)  +
  ggpubr::theme_pubr() +
  theme(text = element_text(size = 24))  +
  xlab("") +
  ylab("PSI")  +
  theme(legend.position = 'none')

## Log2FC UNC13A & STMN2 CE PSI
```{r}
clean_data_table %>% 
  filter(UNC13A_annotated_leaf > 10) %>% 
  filter(STMN2_annotated_leaf > 10) %>% 
  filter(stmn_2_cryptic_psi_leaf > 0 ) %>% 
  filter(unc13a_cryptic_leaf_psi > 0) %>% 
  filter(disease_tissue == T) %>% 
  filter(disease_group2 %in% c("FTLD-TDP","ALS-TDP")) %>% 
  dplyr::select(sample,disease_group2,tissue_clean,stmn_2_cryptic_psi_leaf,unc13a_cryptic_leaf_psi) %>% 
  mutate(log2_unc = log2((unc13a_cryptic_leaf_psi)/(stmn_2_cryptic_psi_leaf)))%>% 
  mutate(tissue_clean = gsub("_","\n",tissue_clean)) %>%

  # mutate(variable = ifelse(grepl("stmn_2",variable), "STMN2", "UNC13A")) %>% 
  ggplot(aes(x = tissue_clean,y = log2_unc, fill = tissue_clean)) + 
  geom_boxplot(position = 'dodge') +
  # geom_jitter(height = 0,width = 0.2,pch = 21) +
  facet_wrap(~disease_group2,scales = "free_x") + 
  theme_bw() + 
  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank()) + 
  theme(text = element_text(size = 24))  +
  xlab("") +
  ylab("PSI")  +
  theme(legend.position =  'top') +
  theme(legend.title=element_blank()) +
  stat_compare_means(comparisons = list(c("STMN2","UNC13A")))
```

@@

clean_data_table %>% 
  filter(disease_tissue == T) %>% 
  filter(disease_group2 %in% c("FTLD-TDP","ALS-TDP")) %>% 
  dplyr::select(sample,tissue_clean,disease_group2,rs12973192,stmn_2_cryptic_psi_leaf,unc13a_cryptic_leaf_psi) %>% 
  mutate(tissue_clean = gsub("_"," ",tissue_clean)) %>% 
  group_by(rs12973192) %>% 
  mutate(n_sample = length(unique(sample))) %>% 
  ungroup() %>% 
  mutate(detection_name = glue::glue("{rs12973192} \n ( {n_sample} )")) %>% 
  ggplot(aes(y = unc13a_cryptic_leaf_psi, x = rs12973192, fill = rs12973192)) + 
  geom_boxplot() + 
  geom_jitter( height = 0) + 
  facet_wrap(~disease_group2,scales = 'free') +
  ylab("UNC13A PSI") +
  xlab("UNC13A rs12973192 Genotype") +
  scale_fill_manual(values = c("#88CCEE","#44AA99","#1B7739")) +
  ggpubr::theme_pubr() +
  theme(text = element_text(size = 24)) +
  stat_compare_means(comparisons = genotype_comparisons,label = "p.signif")

@@

clean_data_table %>% 
  filter(disease_tissue == T) %>% 
  filter(disease_group2 %in% c("FTLD-TDP","ALS-TDP")) %>% 
  dplyr::select(sample,tissue_clean,disease_group2,rs12973192,stmn_2_cryptic_psi_leaf,unc13a_cryptic_leaf_psi) %>% 
  mutate(tissue_clean = gsub("_"," ",tissue_clean)) %>% 
  group_by(rs12973192) %>% 
  mutate(n_sample = length(unique(sample))) %>% 
  ungroup() %>% 
  mutate(detection_name = glue::glue("{rs12973192} \n ( {n_sample} )")) %>% 
  ggplot(aes(y = unc13a_cryptic_leaf_psi, x = rs12973192, fill = rs12973192)) + 
  geom_boxplot() + 
  geom_jitter( height = 0) + 
  facet_wrap(~disease_group2 + tissue_clean,scales = 'free') +
  ylab("UNC13A PSI") +
  xlab("UNC13A rs12973192 Genotype") +
  scale_fill_manual(values = c("#88CCEE","#44AA99","#1B7739")) +
  ggpubr::theme_pubr() +
  theme(text = element_text(size = 24)) +
  stat_compare_means(comparisons = genotype_comparisons,label = "p.signif")

@@

clean_data_table %>% 
  filter(unc13a_cryptic_leaf_psi > 0 ) %>% 
  filter(disease_tissue == T) %>% 
  filter(disease_group2 %in% c("FTLD-TDP","ALS-TDP")) %>% 
  dplyr::select(sample,tissue_clean,disease_group2,rs12973192,stmn_2_cryptic_psi_leaf,unc13a_cryptic_leaf_psi) %>% 
  mutate(tissue_clean = gsub("_"," ",tissue_clean)) %>% 
  group_by(rs12973192) %>% 
  mutate(n_sample = length(unique(sample))) %>% 
  ungroup() %>% 
  mutate(detection_name = glue::glue("{rs12973192} \n ( {n_sample} )")) %>% 
  ggplot(aes(y = unc13a_cryptic_leaf_psi, x = rs12973192, fill = rs12973192)) + 
  geom_boxplot() + 
  geom_jitter( height = 0) + 
  facet_wrap(~disease_group2 + tissue_clean,scales = 'free') +
  ylab("UNC13A PSI") +
  xlab("UNC13A rs12973192 Genotype") +
  scale_fill_manual(values = c("#88CCEE","#44AA99","#1B7739")) +
  ggpubr::theme_pubr() +
  theme(text = element_text(size = 24)) +
  stat_compare_means(comparisons = genotype_comparisons,label = "p.signif")

@@

clean_data_table %>% 
  filter(disease_tissue == T) %>% 
  filter(disease_group2 %in% c("FTLD-TDP","ALS-TDP")) %>% 
  dplyr::select(sample,tissue_clean,disease_group2,rs12973192,stmn_2_cryptic_psi_leaf,unc13a_cryptic_leaf_psi) %>% 
  mutate(tissue_clean = gsub("_"," ",tissue_clean)) %>% 
  ggplot(aes(y = stmn_2_cryptic_psi_leaf, x = rs12973192, fill = rs12973192)) + 
  geom_boxplot() + 
  geom_jitter( height = 0) + 
  facet_wrap(~disease_group2,scales = 'free') +
  ylab("STMN2 PSI") +
  xlab("UNC13A rs12973192 Genotype") +
  scale_fill_manual(values = c("#88CCEE","#44AA99","#1B7739")) +
  ggpubr::theme_pubr() +
  theme(text = element_text(size = 24)) +
  stat_compare_means(comparisons = genotype_comparisons,label = "p.signif")

@@

clean_data_table %>% 
  filter(disease_tissue == T) %>% 
  filter(disease_group2 %in% c("FTLD-TDP","ALS-TDP")) %>% 
  dplyr::select(sample,tissue_clean,disease_group2,rs12973192,stmn_2_cryptic_psi_leaf,unc13a_cryptic_leaf_psi) %>% 
  mutate(tissue_clean = gsub("_"," ",tissue_clean)) %>% 
  ggplot(aes(y = stmn_2_cryptic_psi_leaf, x = rs12973192, fill = rs12973192)) + 
  geom_boxplot() + 
  geom_jitter( height = 0) + 
  facet_wrap(~disease_group2 + tissue_clean,scales = 'free') +
  ylab("STMN2 PSI") +
  xlab("UNC13A rs12973192 Genotype") +
  scale_fill_manual(values = c("#88CCEE","#44AA99","#1B7739")) +
  ggpubr::theme_pubr() +
  theme(text = element_text(size = 24)) +
  stat_compare_means(comparisons = genotype_comparisons,label = "p.signif")

@@

clean_data_table %>% 
  filter(stmn_2_cryptic_psi_leaf > 0 ) %>% 
  filter(disease_tissue == T) %>% 
  filter(disease_group2 %in% c("FTLD-TDP","ALS-TDP")) %>% 
  dplyr::select(sample,tissue_clean,disease_group2,rs12973192,stmn_2_cryptic_psi_leaf,unc13a_cryptic_leaf_psi) %>% 
  mutate(tissue_clean = gsub("_"," ",tissue_clean)) %>% 
  ggplot(aes(y = stmn_2_cryptic_psi_leaf, x = rs12973192, fill = rs12973192)) + 
  geom_boxplot() + 
  geom_jitter( height = 0) + 
  facet_wrap(~disease_group2 + tissue_clean,scales = 'free') +
  ylab("STMN2 PSI") +
  xlab("UNC13A rs12973192 Genotype") +
  scale_fill_manual(values = c("#88CCEE","#44AA99","#1B7739")) +
  ggpubr::theme_pubr() +
  theme(text = element_text(size = 24)) +
  stat_compare_means(comparisons = genotype_comparisons,label = "p.signif")

@@

clean_data_table %>% 
  filter(disease_tissue == T) %>% 
  filter(grepl("Cortex",tissue_clean)) %>% 
  filter(disease_group2 %in% c("FTLD-TDP","ALS-TDP")) %>% 
    mutate(rs12973192 = fct_relevel(rs12973192,
                              "C/C", "C/G", "G/G")) %>%
  filter(!grepl("Cord",tissue_clean)) %>% 
  mutate(log10_stmn2 = log10(stmn_2_cryptic_psi_leaf)) %>% 
    mutate(log10_unc13a = log10(unc13a_cryptic_leaf_psi)) %>% 
    ggpubr::ggscatter(., 
                      x = "log10_stmn2",
                      y = "log10_unc13a",
                      color = 'rs12973192',                      
                      add = "reg.line", size = 3
                      ) +
    ylab("UNC13A CE PSI ") + 
    xlab("STMN2 Cryptic PSI ") +
  stat_cor(aes( x = stmn_2_cryptic_psi_leaf,
                      y = unc13a_cryptic_leaf_psi,
                      color = rs12973192),
           method = 'spearman',
           cor.coef.name = 'rho',
           show.legend = FALSE,
           size = 14) + 
    scale_color_manual(values = c("#88CCEE","#44AA99","#1B7739")) +
  theme(legend.title = element_blank()) +
  theme(text = element_text(size = 24),legend.text = element_text(size = 32))

@@

## Log2 Fold UNC / STMN2 CE in TDP-path with both detected - rs12973192 - cortex only

```{r}
detected_table_for_graph = clean_data_table %>% 
  filter(disease_group2 %in% c("FTLD-TDP","ALS-TDP")) %>% 
  filter(unc13a_cryptic_leaf_psi > 0 ) %>% 
  filter(stmn_2_cryptic_psi_leaf > 0 ) %>% 
  filter(grepl("Cortex",tissue_clean)) %>% 
  filter(disease_tissue == T) %>% 
  filter(disease_group2 %in% c("FTLD-TDP","ALS-TDP")) %>% 
  dplyr::select(sample,tissue_clean,disease_group2,rs12973192,rs12608932,stmn_2_cryptic_psi_leaf,unc13a_cryptic_leaf_psi) %>% 
  mutate(log2_unc = log2((unc13a_cryptic_leaf_psi)/(stmn_2_cryptic_psi_leaf))) %>% 
  mutate(tissue_clean = gsub("_","\n",tissue_clean)) %>% 
  group_by(rs12973192) %>% 
  mutate(n_sample = length(unique(sample))) %>% 
  ungroup() %>% 
  mutate(detection_name = glue::glue("{rs12973192} \n ( {n_sample} )")) %>% 
  mutate(no_cong = ifelse(rs12608932 == "C/C" & rs12973192 == "C/G",8,3))

comparisons = combn(unique(detected_table_for_graph$detection_name),2,simplify = F)

detected_table_for_graph %>% 
  ggplot(aes(y = log2_unc, x = detection_name,fill = detection_name)) + 
  geom_boxplot(show.legend = F) + 
  geom_jitter(show.legend = F, alpha = 0.8, height = 0,pch = 21) + 
  stat_compare_means( label = "p.format") + 
  stat_compare_means(aes(group = detection_name),comparisons = comparisons,label = "p.signif") +
  ylab("Ratio UNC13A CE PSI / STMN2 PSI") + 
  ylab(expression(paste("Lo", g[2], " fold UNC13A CE PSI / STMN2 CE PSI "))) +
  xlab("UNC13A rs12973192 Genotype") +
  scale_fill_manual(values = c("#88CCEE","#44AA99","#1B7739")) +
  ggpubr::theme_pubr() +
  theme(text = element_text(size = 24)) +
  geom_hline(yintercept = 0,size = 1.5) 
```

## Log2 Fold UNC / STMN2 CE in TDP-path with both detected - rs12973192 - cortex and cord =

```{r}
detected_table_for_graph = clean_data_table %>% 
  filter(disease_group2 %in% c("FTLD-TDP","ALS-TDP")) %>% 
  filter(unc13a_cryptic_leaf_psi > 0 ) %>% 
  filter(stmn_2_cryptic_psi_leaf > 0 ) %>% 
  filter(disease_tissue == T) %>% 
  filter(disease_group2 %in% c("FTLD-TDP","ALS-TDP")) %>% 
  dplyr::select(sample,tissue_clean,disease_group2,rs12973192,rs12608932,stmn_2_cryptic_psi_leaf,unc13a_cryptic_leaf_psi) %>% 
  mutate(log2_unc = log2((unc13a_cryptic_leaf_psi)/(stmn_2_cryptic_psi_leaf))) %>% 
  mutate(tissue_clean = gsub("_","\n",tissue_clean)) %>% 
  group_by(rs12973192) %>% 
  mutate(n_sample = length(unique(sample))) %>% 
  ungroup() %>% 
  mutate(detection_name = glue::glue("{rs12973192} \n ( {n_sample} )")) %>% 
  mutate(no_cong = ifelse(rs12608932 == "C/C" & rs12973192 == "C/G",8,3))

comparisons = combn(unique(detected_table_for_graph$detection_name),2,simplify = F)
